IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-11-13 main.tex
:books: Update reference

			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}. In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}. This conclusion is summarized below.

@@

			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$. The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.

@@

			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes. Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$. To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. Similarly, no loss is introduced by SDR and local optimality is guaranteed. The proofs are omitted here. Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}. Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.

@@

			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}. The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.

@@

		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$. Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above because of the unit-modulus constraint \eqref{co:irs_modulus}. Thus, Algorithm~\ref{al:sca} is guaranteed to converge. Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}. Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem. According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
		\end{subsection}

>>>>

			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}. In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}. This conclusion is summarized below.

@@

			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$. The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010b}.

@@

			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes. Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$. To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. Similarly, no loss is introduced by SDR and local optimality is guaranteed. The proofs are omitted here. Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010b}. Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.

@@

			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}. The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010b}.

@@

		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$. Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above because of the unit-modulus constraint \eqref{co:irs_modulus}. Thus, Algorithm~\ref{al:sca} is guaranteed to converge. Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978a}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}. Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem. According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
		\end{subsection}
